---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fuzzr

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Travis-CI Build Status](https://travis-ci.org/mdlincoln/fuzzr.svg?branch=master)](https://travis-ci.org/mdlincoln/fuzzr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdlincoln/fuzzr?branch=master&svg=true)](https://ci.appveyor.com/project/mdlincoln/fuzzr)


fuzzr implements some simple ["fuzz tests"](https://en.wikipedia.org/wiki/Fuzz_testing) for your R functions, passing in a wide array of inputs and returning a report (normally as a data.frame) on how your function reacts.

## Installation

```{r, eval = FALSE}
devtools::install_github("mdlincoln/fuzzr")
```

## Usage

Evaluate a function argument by supplying it's quoted name along with the tests to run to `fuzz_function`, along with any other required static values. 
`fuzz_function` returns a "fuzz_results" object that stores conditions raised by a function (message, warning, or error) along with any value returned by that function.
You can preview this list with 

```{r}
library(fuzzr)
fuzz_results <- fuzz_function(fun = lm, arg_name = "subset", data = iris, 
                              formula = Sepal.Length ~ Petal.Width + Petal.Length, 
                              tests = test_all())

as.data.frame(fuzz_results)

model <- value_returned(fuzz_results, "int_multiple")
coefficients(model)
```

### Tests

Tests are set by passing functions that return named lists of input values.
These values will be passed as function arguments.
Several default suites are provided with this package, such as `test_char`, however you may implement your own by passing a function that returns a similarly-formatted list.

```{r}
test_char()
```

---
[Matthew Lincoln](http://matthewlincoln.net)
