---
title: "fuzzr: Fuzz-Testing for R Functions"
author: "Matthew Lincoln"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

R's type-leniency is a blessing and a curse.
This means it is up to the programmer to judge (or not) which inputs should be accepted, and which should throw errors.
fuzzr helps you to check how cleanly and informatively your function responds to unexpected input.

Say we build a function that takes a single string and a single integer, repeats the string that number of times, and pastes it together using a given delimiter:

```{r}
my_function <- function(x, n, delim = " - ") {
  paste(rep(x, n), collapse = delim)
}

my_function("fuzz", 7)
```

Simple enough.
However, this function quickly breaks if we pass in somewhat unexpected values:

```{r, error = TRUE, purl = FALSE}
my_function("fuzz", "bar")
```

Let's test this with a full battery of fuzz tests:

```{r, results = "asis"}
library(fuzzr)
# Note that, while we are specifically fuzz testing the 'n' argument, we still 
# need to provide an 'x' argument to pass along to my_function(). We do not have
# to supply a delimiter, as my_function() declares a default value for this
# argument.
my_fuzz_results <- fuzz_function(my_function, "n", x = 1:3, tests = test_all(), test_delim = ";")

# Produce a data frame summary of the results
fuzz_df <- as.data.frame(my_fuzz_results)
knitr::kable(fuzz_df)
```

Almost any of the unexpected values for `n` throw the farily generic warning `invalid 'times' argument`, which really comes from the `rep` function.
Some types, like doubles, factors, and even dates (!) don't throw errors, but instead return a result.
We can check the value of that result with `fuzz_value()`, and the call originating it with `fuzz_call()`:

```{r}
fuzz_call(my_fuzz_results, which.max(fuzz_df$n == "dbl_single"))
fuzz_value(my_fuzz_results, which.max(fuzz_df$n == "dbl_single"))

fuzz_call(my_fuzz_results, which.max(fuzz_df$n == "date_single"))
# Hm, dates can be coerced into very large integers. Let's see how long this
# result is.
nchar(fuzz_value(my_fuzz_results, which.max(fuzz_df$n == "date_single")))
# Oh dear.
```

Perhaps we might chose to enforce this with a tailored type check (using [assertthat](https://cran.r-project.org/package=assertthat)) that catches unexpected values and produces a more informative error message. 

```{r, results = "asis"}
my_function_2 <- function(x, n, delim = " - ") {
  assertthat::assert_that(assertthat::is.count(n))
  paste(rep(x, n), collapse = delim)
}

# We will abbreviate this check by only testing against double and date vectors
fuzz_df_2 <- as.data.frame(fuzz_function(my_function_2, "n", x = "fuzz", 
                                         tests = c(test_dbl(), test_date())))

knitr::kable(fuzz_df_2)
```

## Fuzzing multiple arguments

`fuzz_function` works by mapping several test inputs over one argument of a function while keeping the other arguments static.
`p_fuzz_function` lets you specify a battery of tests for each variable, and then runs every combination of test.
This takes a named list of arguments and the tests to be run on them. These tests can be specified using the provided functions like `test_char`, or with variable inputs you provide.
Remember that each test condition must, itself, be named.

```{r, results = 'asis'}
p_args <- list(
  x = list(
    simple_char = "test",
    numbers = 1:3
  ),
  n = test_all(),
  delim = test_all())

pr <- p_fuzz_function(my_function_2, p_args)
prdf <- as.data.frame(pr)

knitr::kable(head(prdf))
```

